### 2020-06-10 chapters/background.tex
Footnotes

Distinguishing between batch and stream processing is important to understand how a monitoring system on top of the latter would work. The Venn diagram \ref{fig:stream-superset} \cite{batch-is-a-special-case-of-streaming} illustrates the relation of both processing techniques. A data stream is unbounded or infinite while a bounded data stream has a beginning and an end. Using these definitions, the concept of an unbounded data stream contains that of a bounded data set. That is, from an infinite stream, it is possible to fix a left and right limits in order to obtain a bounded and finite data set. This relation is visible in Figure \ref{fig:unbounded-bounded-superset} \cite{batch-is-a-special-case-of-streaming}.

>>>>

Distinguishing between batch and stream processing is important to understand how a monitoring system on top of the latter would work. The Venn diagram \ref{fig:stream-superset} from a blog post by Ververica \footnote{https://www.ververica.com/blog/batch-is-a-special-case-of-streaming} illustrates the relation of both processing techniques. A data stream is unbounded or infinite while a bounded data stream has a beginning and an end. Using these definitions, the concept of an unbounded data stream contains that of a bounded data set. That is, from an infinite stream, it is possible to fix a left and right limits in order to obtain a bounded and finite data set. This relation is visible in Figure \ref{fig:unbounded-bounded-superset} from the same blog post.

### 2020-06-10 chapters/introduction.tex
Footnotes

\section{Context} \label{sec:context}
In the past decade, applications have become increasingly data-driven, placing data at the center of application design. Different use cases process data in different ways for different purposes. For instance, e-commerce platforms need to process a large number of transactions, for example, those made daily by all Alibaba's\footnote{https://alibaba.com} clients, while ensuring that sales run smoothly and that products are delivered to customers' homes. Streaming services, like YouTube\footnote{https://youtube.com} and Netflix\footnote{https://netflix.com}, try to guarantee that media content reaches up to millions of users simultaneously. This media content may have been previously recorded and stored, or may be generated on the fly. Social networks are also responsible for generating large volumes of data. A social network like Twitter\footnote{https://twitter.com}, for example, generates more than 500 million \textit{tweets} (posts in Twitter) per day \cite{twitter-throughput}. \textit{Tweets} may contain text, media content or both. Cybersecurity applications are yet another example of time-sensitive, data-driven applications. These need to monitor user accesses and their actions in the network, where timely detection of intruders is critical to prevent them from tampering with the protected system.

>>>>

\section{Context} \label{sec:context}
In the past decade, applications have become increasingly data-driven, placing data at the center of application design. Different use cases process data in different ways for different purposes. For instance, e-commerce platforms need to process a large number of transactions, for example, those made daily by all Alibaba's\footnote{https://alibaba.com} clients, while ensuring that sales run smoothly and that products are delivered to customers' homes. Streaming services, like YouTube\footnote{https://youtube.com} and Netflix\footnote{https://netflix.com}, try to guarantee that media content reaches up to millions of users simultaneously. This media content may have been previously recorded and stored, or may be generated on the fly. Social networks are also responsible for generating large volumes of data. A social network like Twitter\footnote{https://twitter.com}, for example, generates more than 500 million \textit{tweets} (posts in Twitter) per day\footnote{$https://blog.twitter.com/engineering/en_us/a/2013/new-tweets-per-second-record-and-how.html$}. \textit{Tweets} may contain text, media content or both. Cybersecurity applications are yet another example of time-sensitive, data-driven applications. These need to monitor user accesses and their actions in the network, where timely detection of intruders is critical to prevent them from tampering with the protected system.
